Spin canonical divisors of log stacky curves

### 2015-06-21 stacky_write_up/spin_cring.tex
add additional hypotheses to base case lemma

\begin{thm}

\label{thm:ram_order_ind}
Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
			\neq y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 7, 7; 0), J_4 = \{2, 3\}$
	\item[(e)] $\sigma_5 = (0; 7, 7, 7; 0), J_5 = \{1, 2, 3\}$
	\item[(f)] $\sigma_6 = (0; 3, 3, 3, 5; 0), J_6 = \{4\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 5, 5; 0), J_7 = \{3, 4\}$
	\item[(h)] $\sigma_8 = (0; 3, 5, 5, 5; 0), J_8 = \{2, 3, 4\}$
	\item[(i)] $\sigma_9 = (0; 5, 5, 5, 5; 0), J_9 = \{1, 2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 3, 3, 3, 3, 3; 0), J_{10} = \{1, 2, 3, 4, 5\}$
\end{enumerate}
\end{lem}

@@

Furthermore, each case satisfies (Ad-iii) as demonstrated below.
Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$ are
independent of the choice of $i$.

>>>>

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
			\neq y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 7, 7; 0), J_4 = \{2, 3\}$
	\item[(e)] $\sigma_5 = (0; 7, 7, 7; 0), J_5 = \{1, 2, 3\}$
	\item[(f)] $\sigma_6 = (0; 3, 3, 3, 5; 0), J_6 = \{4\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 5, 5; 0), J_7 = \{3, 4\}$
	\item[(h)] $\sigma_8 = (0; 3, 5, 5, 5; 0), J_8 = \{2, 3, 4\}$
	\item[(i)] $\sigma_9 = (0; 5, 5, 5, 5; 0), J_9 = \{1, 2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 3, 3, 3, 3, 3; 0), J_{10} = \{1, 2, 3, 4, 5\}$
\end{enumerate}

\noindent
Furthermore, $R'$ satisfies the hypothesis of Theorem ~\ref
{thm:ram_order_ind}(d), which asserts that for all $i \in J$, $e_i >
\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
(as defined in Theorem ~\ref{thm:ram_order_ind}(c)) then
$in_\prec(I')$ is minimally generated by products of two monomials.
\end{lem}

@@

Furthermore, each case satisfies (Ad-iii) as demonstrated below.
Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ are
independent of the choice of $i$.
